
1- Loads data and sets up a survey design.
2- Bootstraps samples per survey year (2004, 2013, 2023) with weighted duplication based on wc.
3- Fits a logistic regression model with fractional polynomials (age) + year effect for each bootstrap.
4- Computes age-dependent prevalence P(a, t) and incidence λ(a, t) curves.
5- Summarizes bootstrap results (median & 95% CI) and exports them to Excel.

# Load libraries
```{r}
library(tidyverse)
library(survey)
library(openxlsx)
library(mfp)
library(here)
library(readr)
options(warn=-1)
library(writexl)

```
# Load datasets
```{r, include=FALSE, warning=F}
coq_combined <- read_csv(here("final", "Coq_combined.csv"))
```

```{r}
# Set parameters for bootstrapping
n_bootstrap <- 2000  # Number of bootstrap samples
sample_size_2004 <- nrow(coq_combined[coq_combined$edit == 2004, ])
sample_size_2013 <- nrow(coq_combined[coq_combined$edit == 2013, ])
sample_size_2023 <- nrow(coq_combined[coq_combined$edit == 2023, ])

data_2004 <- coq_combined[coq_combined$edit == 2004, ]
data_2013 <- coq_combined[coq_combined$edit == 2013, ]
data_2023 <- coq_combined[coq_combined$edit == 2023, ]

# Initialize lists to store bootstrap samples for each year
bootstrap_samples_2004 <- vector("list", n_bootstrap)
bootstrap_samples_2013 <- vector("list", n_bootstrap)
bootstrap_samples_2023 <- vector("list", n_bootstrap)

concatenated_bootstrap_samples <- vector("list", n_bootstrap)
# Function to generate a bootstrap sample based on survey weight duplication
generate_and_sort_bootstrap <- function(data, sample_size) {
  # Duplicate individuals based on survey weights
  weighted_data <- data[rep(seq_len(nrow(data)), data$wc), ]
  
  # Assign a random number to each individual
  weighted_data$random_number <- runif(nrow(weighted_data))
  
  # Sort by survey year ('edit') and the random number
  weighted_data <- weighted_data %>% arrange(edit, random_number)
  
  # Select the first n individuals to form the sample
  sampled_data <- head(weighted_data, sample_size)
  
  return(sampled_data)
}

# Generate bootstrap samples
for (i in 1:n_bootstrap) {
  bootstrap_samples_2004[[i]] <- generate_and_sort_bootstrap(data_2004, sample_size_2004)
  bootstrap_samples_2013[[i]] <- generate_and_sort_bootstrap(data_2013, sample_size_2013)
  bootstrap_samples_2023[[i]] <- generate_and_sort_bootstrap(data_2023, sample_size_2023)
  
  concatenated_bootstrap_samples[[i]] <- rbind(bootstrap_samples_2004[[i]], 
                                                bootstrap_samples_2013[[i]], 
                                                bootstrap_samples_2023[[i]])
}

```


```{r}
# Define functions to calculate prevalence and incidence

calculate_prevalence <- function(sample) {
  # Logistic regression with fractional polynomials
  sample$age_1 <- (sample$age / 10)^0.5
  sample$age_2 <- (sample$age / 10)

  ps_combined <- svydesign(ids = ~ nqes+cserv, strata=~ville_num,weights = ~ wc, data = sample,nest=TRUE)

  ps_combined$variables$edit <- factor(ps_combined$variables$edit, levels = c("2004", "2013", "2023"))
  ps_combined$variables$edit <- relevel(ps_combined$variables$edit, ref = "2004")

  modello1_fp <- svyglm(antihcv ~ age_1 + age_2 + edit, 
                      design = ps_combined, 
                      family = binomial(link = "logit"))

  coefficients <- coef(modello1_fp)

# Assign coefficients to variables
  alpha <- coefficients["(Intercept)"]
  age_1_coeff <- coefficients["age_1"]
  age_2_coeff <- coefficients["age_2"]
  edit2013  <- coefficients["edit2013"]
  edit2023  <- coefficients["edit2023"]

  return(list(
    alpha = alpha,
    age_1_coeff = as.numeric(age_1_coeff),
    age_2_coeff = as.numeric(age_2_coeff),
    edit2013 = as.numeric(edit2013),
    edit2023 = as.numeric(edit2023)
  ))  # Replace with actual prevalence calculation if needed
}

#compute fractional polynomial η(age) --> (see SI paper)
eta <- function(a) {
  
  coeff_I1 <- as.numeric(prevalence$age_1_coeff)
  coeff_I2 <- as.numeric(prevalence$age_2_coeff)
  return((coeff_I1 * (a / 10)^0.5) + coeff_I2 * (a / 10))
}

# First derivative of η(age)
eta_first <- function(a) {
  coeff_I1 <- as.numeric(prevalence$age_1_coeff)
  coeff_I2 <- as.numeric(prevalence$age_2_coeff)
  return(((coeff_I1 * 0.5 / sqrt(10)) / sqrt(a)) + (coeff_I2 / 10))
}
# Age-dependent prevalence function
P<- function(a, t) {
  α <- as.numeric(prevalence$alpha)
  c1 <- as.numeric(prevalence$edit2013)
  c2 <- as.numeric(prevalence$edit2023)
  
  if (t == 2004) {
    return(exp(α + eta(a)) / (1 + exp(α + eta(a))))
  } else if (t == 2013) {
    return(exp(α + eta(a) + c1) / (1 + exp(α + eta(a) + c1)))
  } else if (t == 2023) {
    return(exp(α + eta(a) + c2) / (1 + exp(α + eta(a) + c2)))
  } else {
    stop("Year must be 2004, 2013, or 2023.")
  }
}
# Age-dependent incidence function
λ <- function(a, t) {
  #Distribution from Leon et al 2016, ref table 2 main paper
  #seroreversion and clerance
  γ <- rbinom(1, nrow(coq_combined), 0.001) / nrow(coq_combined)
  γ_first <- rbinom(1, nrow(coq_combined), 0.0048) / nrow(coq_combined)
  γ_sec <- rbinom(1, nrow(coq_combined), 0.0048) / nrow(coq_combined)
  #Death rate
  μ1 <- rpois(1, 22)/1000


  if (t==2004){
    #DU that recived treatments
    x<-0
    y<-0
    #yearly proportion of new drug users
    β <- runif(1, 0.01, 0.03)
    }
  if (t==2013){
    #DU that recived treatments
    x<-0.09
    y<-0
    #yearly proportion of new drug users
    β <- runif(1, 0.01, 0.03)
  }
    if (t==2023){
    #DU that recived treatments
    x<-0.18
    y<-0.227
    #yearly proportion of new drug users
    β <- runif(1, 0.01, 0.022)}
  
  p_value <- P(a, t)
  inc <- (eta_first(a) * p_value * (1 - p_value) + (β - μ1) - (β - μ1 - γ *(1-x-y) - γ_first*x - γ_sec*y) * p_value) / (1 - p_value)
  return(inc * 100)
}

# Storage lists for prevalence and incidence values
prevalences <- numeric(n_bootstrap * 3)


lambda_2004_samples <- list()
lambda_2013_samples <- list()
lambda_2023_samples <- list()

# Run bootstrap prevalence and incidence estimation across 2000 samples
for (i in 1:n_bootstrap) {
  # Calculate prevalence for each year and store
  prevalence <- calculate_prevalence(concatenated_bootstrap_samples[[i]])

  a_values <- seq(18, 55, length.out = 1000)
  lambda_values_2004 <- λ(a_values, t = 2004)
  lambda_values_2013 <- λ(a_values,  t = 2013)
  lambda_values_2023 <- λ(a_values,  t = 2023)
  
  lambda_2004_samples[[i]] <- lambda_values_2004
  lambda_2013_samples[[i]] <- lambda_values_2013
  lambda_2023_samples[[i]] <- lambda_values_2023
}


# Convert the lists to data frames for easier manipulation and summary
lambda_2004_df <- do.call(cbind, lambda_2004_samples)
lambda_2013_df <- do.call(cbind, lambda_2013_samples)
lambda_2023_df <- do.call(cbind, lambda_2023_samples)

# Calculate row-wise statistics for each year
lambda_2004_summary <- data.frame(
  a_values = a_values,
  median = apply(lambda_2004_df, 1, median),
  lower_95 = apply(lambda_2004_df, 1, quantile, probs = 0.025),
  upper_95 = apply(lambda_2004_df, 1, quantile, probs = 0.975)
)

lambda_2013_summary <- data.frame(
  a_values = a_values,
  median = apply(lambda_2013_df, 1, median),
  lower_95 = apply(lambda_2013_df, 1, quantile, probs = 0.025),
  upper_95 = apply(lambda_2013_df, 1, quantile, probs = 0.975)
)

lambda_2023_summary <- data.frame(
  a_values = a_values,
  median = apply(lambda_2023_df, 1, median),
  lower_95 = apply(lambda_2023_df, 1, quantile, probs = 0.025),
  upper_95 = apply(lambda_2023_df, 1, quantile, probs = 0.975)
)


# Append the summary statistics as new columns in the original datasets
lambda_2004_df <- cbind(lambda_2004_df, 
                        median = lambda_2004_summary$median, 
                        lower_95 = lambda_2004_summary$lower_95, 
                        upper_95 = lambda_2004_summary$upper_95)

lambda_2013_df <- cbind(lambda_2013_df, 
                        median = lambda_2013_summary$median, 
                        lower_95 = lambda_2013_summary$lower_95, 
                        upper_95 = lambda_2013_summary$upper_95)

lambda_2023_df <- cbind(lambda_2023_df, 
                        median = lambda_2023_summary$median, 
                        lower_95 = lambda_2023_summary$lower_95, 
                        upper_95 = lambda_2023_summary$upper_95)


```

```{r}

# Save the results_df data frame as an Excel file
# Ensure lambda_2004_df is a data frame
lambda_2004_df <- as.data.frame(lambda_2004_df)
lambda_2013_df <- as.data.frame(lambda_2013_df)
lambda_2023_df <- as.data.frame(lambda_2023_df)


# Save the data frame as an Excel file
write_xlsx(lambda_2004_df, here("final", "incidence_bootstrap_04.xlsx"))
write_xlsx(lambda_2013_df, here("final", "incidence_bootstrap_13.xlsx"))
write_xlsx(lambda_2023_df, here("final", "incidence_bootstrap_23.xlsx"))
```


